### 2019-03-30 stableLimit.tex
change stableLimit.tex

@@

\subsection{Background}
    The study of the asymptotic behavior of critical branching particle systems has a long history.
	It is well known that for a critical Galton-Watson 
    %process $(Z_n)$, 
    process $\{(Z_n)_{n = 0,1,\dots}; P\}$,	
	we have
	\[\label{eq: Kolmogorov's result with finite variance}
		n P(Z_n > 0)
		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
	\]
	and
	\[\label{eq: Yaglom's result with finite variance}
		\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
		\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
	\]
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

    %Note that 
    Notice that, see \cite{KestenNeySpitzer1966The-Galton-Watson} for example,
    \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, so a more appropriate scaling is needed.
	This was first obtained by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson 
	%process $(Z_n)$ 
	process $\{(Z_n)_{n = 0,1,\dots}; P\}$
	with infinite variance.
	Assuming that 
	%the offspring generating function $f(s)$ 
	the corresponding offspring generating function $f(s)$
	is of the form
\[\label{eq: offspring generating function with alpha moment}
	f(s)
	= s + (1-s)^{1+ \alpha} l(1-s),
	\quad s\geq 0,
\]
	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$, then
\[ \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0) = n^{-1/\alpha} L(n),
\]
	where $L$ is a slowly varying function at $\infty$, and
\[\label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\]
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
\[
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\]
	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} considered the converse of this problem:
	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must be of  the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	%Denote by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the corresponding offspring probability generating function,
	%and  by $\mathbf F_n(\mathbf s), \quad n>1$ its iterates.
	and  by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right principal  eigenvectors respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	%\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and 
	%the matrix $E(\mathbf s)$ is defined by
	the matrix $G(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s)
	%= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\]
    Let 
    %$a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, 
    $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$,
    with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
It was shown in \cite{GoldsteinHoppe1978Critical} that,
 for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
\]
	and for each $\mathbf j \in \mathbb N_0^d$,
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\]
%new
    where $\mathbf z^{(\alpha)}$ is Zolotarev's random variable with index $\alpha$. 
%end new
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time mutitype critical Galton-Watson processes.

	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
%deleted	
	%(see \cite[Section 6.3]{AsmussenHering1983Branching} and \cite[Section 6.4]{AsmussenHering1983Branching}).
%end deleted
	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite[Theorem~4.2]{AsmussenHering1983Branching} for critical branching Markov processes.
%deleted    
    %see \cite[Theorem 4.2]{AsmussenHering1983Branching}.
%end deleted

    In this paper, we are interested in a class of measure-valued branching Markov process known as $(\xi, \psi)$-superprocesses:
    $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact, separable, metric space $E$; 
    $\psi$, the branching mechanism of the superprocess, 
    %is function $\psi$ on $E \times [0,\infty)$ of the form
    is a function on $E \times [0,\infty)$ of the form
\[ \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\]
	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
	In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.

	Results parallel to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to  
	a class of critical superprocesses with general branching mechanism and general spatial motions:
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition,
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(X_t \not \equiv 0)
	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
	$\mathbf e$ is an exponential random variable with mean $1$;
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	A simpler
	version of this question has already been answered in the context of continuous-state branching processes %(CSBP) 
	(CSBPs)
	which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered 
	%CSBP's $(Y_t)$ 
	CSBPs $\{(Y_t); P\}$
	with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\]
%new
    where $\mathbf z^{(\gamma - 1)}$ is Zolotarev's random variable with index $\gamma - 1$.
%end new
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied 
	%CSBP's 
	CSBPs $\{(Y_t); P\}$
	with branching mechanism
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0.
\]
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ 
	satisfying Grey's condition.
	In order for the left side of \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for 
	%some positive function $(\lambda_t)$,
	some positive constants $(\lambda_t)_{t\geq 0}$, 
	one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

In this paper, we will establish a result parallel
	to \eqref{eq: conditional limit of CSBP with stable branching} for some 
   critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ 
	with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and 
	%is regularly varying with index $\frac{1}{\gamma_0 - 1}$ at $\infty$..
	is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
\[
	\mathbf P_{\delta_x}( X_t \not \equiv 0)
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
\]
	and for a large class of non-negative testing functions $f$,
\[\label{eq: result2}
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\]
	%where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$.
	Precise statements of the assumptions and the results are presented in the next 
	%subsection.
	section.
    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ 
    %depend 
    depends primarily on the lowest index $\gamma_0$.

@@

	%We first note that, 

@@

	%We then note that, from the definition of $J'_G, J'_g$ and $\eta_t$, we have

>>>>

%%%----Versions-----------------------------
%stable-limit4.tex 2018/6/21  by Yanxia-------
%stable-limit3.tex 2018/6/13  by Zhenyao-------

@@

\subsection{Background}
    The study of the asymptotic behavior of critical branching particle systems has a long history.
	It is well known that for a critical Galton-Watson
    %process $(Z_n)$,
    %YX process $\{(Z_n)_{n = 0,1,\dots}; P\}$,	
    process $\{(Z_n)_{n\geq 0}; P\}$,	
	we have
	\[\label{eq: Kolmogorov's result with finite variance}
		n P(Z_n > 0)
		\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
	\]
	and
	\[\label{eq: Yaglom's result with finite variance}
		\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
		\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
	\]
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
	Since then, lots of analogous results were obtained for more general critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

    %YX Notice that, see \cite{KestenNeySpitzer1966The-Galton-Watson} for example,
     Notice that,
    \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid
  %YX    even if the 2nd moment is infinite, i.e., $\sigma^2 = \infty$.
   even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate,
    %YX so a more appropriate scaling is needed.
    and then  more appropriate scalings are needed.
	%YX This was first obtained
Research in this direction was first gaven
by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up,
	which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance:  Consider a critical Galton-Watson
	%process $(Z_n)$
	%YX process $\{(Z_n)_{n = 0,1,\dots}; P\}$
    process $\{(Z_n)_{n\geq 0}; P\}$
	with infinite variance.
%YX	Assuming that  the corresponding offspring generating function $f(s)$
Assume that the  generating function $f(s)$ of the offspring distribution
	is of the form
\[\label{eq: offspring generating function with alpha moment}
	f(s)
	= s + (1-s)^{1+ \alpha} l(1-s),
	\quad s\geq 0,
\]
	where $l$ is a slowly varying function at $0$ and $0 < \alpha \leq 1$.
%YX , then
Then
\[ \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0) = n^{-1/\alpha} L(n),
\]
	where $L$ is a slowly varying function at $\infty$, and
\[\label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\]
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
\[
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\]
	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} considered the converse of this problem:
	In order $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have a non-degenerate weak limit, the offspring generating function must be of  the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	 Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the corresponding offspring probability generating function,
	and  by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right principal  eigenvectors respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and
	the matrix $G(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\]
    Let
    $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$,
    with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
It was shown in \cite{GoldsteinHoppe1978Critical} that,
 for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
\]
	and for each $\mathbf j \in \mathbb N_0^d$,
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\]
  %YX  where $\mathbf z^{(\alpha)}$ is a Zolotarev's random variable with index $\alpha$.
  where $\mathbf z^{(\alpha)}$ is a random variable with  Zolotarev's distribution with index  $\alpha$.
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time mutitype critical Galton-Watson processes.

	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in \cite[Theorem~4.2]{AsmussenHering1983Branching} for critical branching Markov processes.

    In this paper, we are interested in a class of measure-valued branching Markov process known as $(\xi, \psi)$-superprocesses:
    $\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact, separable, metric space $E$;
    $\psi$, the branching mechanism of the superprocess,
    is a function on $E \times [0,\infty)$ of the form
\[ \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\]
	where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.
	In the next subsection, we will give a more precise description of $(\xi, \psi)$-superprocesses.

	Results parallel to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses with branching mechanism of the form $(x,z)\mapsto z^2$ and with the spatial motion satisfying some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} extended the results of \cite{EvansPerkins1990Measure-valued} to
	a class of critical superprocesses with general branching mechanism and general spatial motions:
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from 
%YX a measure $\mu$.
a finite measure $\mu$ on $E$.
	Suppose the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism $\psi$ satisfies the following second moment condition,
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
%YX new added
For any finite measure $\mu$ on $E$ and
any measurable function $f$ on $E$, we use $\langle f,\mu\rangle$	 to denote the integral of $f$ with respect to $\mu$. 
Put $\|\mu\|=\langle 1, \mu\rangle$.
%end new
	Under some other mild assumptions, it was proved in  \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
%Yx in the following "X_t \not \equiv 0" is replaced by "\|\mu\|\neq 0" without noticing
	t \mathbf P_\mu(\|X_t\| \neq 0)
	\xrightarrow[t\to \infty]{} c^{-1} 
%YX \langle \phi, \mu \rangle_m,
\langle \phi, \mu \rangle,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot |\|X_t\| \neq 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
%YX new added
$\langle\cdot, \cdot \rangle$ denotes the inner product in $L^2(E, m)$;
%end new
	$\mathbf e$ is an exponential random variable with mean $1$;
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
	In \cite{RenSongSun2017Spine},  we %YX also
provided an alternative probabilistic approach to \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	A simpler
	version of this question has already been answered in the context of continuous-state branching processes
	(CSBPs)
	which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered
	CSBPs $\{(Y_t)_{t\geq 0}; P\}$
	with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\]
    where $\mathbf z^{(\gamma - 1)}$ is
    %a Zolotarev's random variable with index $\gamma - 1$.
    a random variable with Zolotarev's distribution with index $\gamma - 1$.
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
	CSBPs $\{(Y_t)_{t\ge 0}; P\}$
	with branching mechanism
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0.
\]
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$
	satisfying Grey's condition.
	In order for the left side of \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for
	some positive constants $(\lambda_t)_{t\geq 0}$,
	one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

In this paper, we will establish a result parallel
	to \eqref{eq: conditional limit of CSBP with stable branching} for some
   critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$
	with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ converges to $0$ as $t\to \infty$ and
	is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
\[
	\mathbf P_{\delta_x}( \|X_t\| \neq0)
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
\]
	and for a large class of non-negative testing functions $f$,
\[\label{eq: result2}
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\]
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a Zolotarev's random variable with index $\gamma_0 - 1$.
	Precise statements of the assumptions and the results are presented in the next
		section.
    It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$   depends primarily on the lowest index $\gamma_0$.

@@

@@
